### 2013-06-13 Tex/chapters/model.tex
Einleitung zu Graphen geschrieben

%~ \subsubsection{Graphs}
    %~ A graph is a set of nodes \(V\) and edges \(E\).
\subsection{Gabriel- and Relative Neighborhood Graph}
\label{ssec:graphtypes}
    The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
    Delaunay Triangulation. Two nodes \(i\) and \(j\) with distance
    \(d_{ij}\) are connected with an edge if a circle with it's
    center on the middlepoint between \(i\) and \(j\) and radius
    \(r = \frac d 2\) contains no other nodes. This area will be
    called \emph{lune} in the following. See also Figure
    \ref{fig:lunes}\subref{sfig:lunes:def}.\\
    The Relative Neighborhood Graph \cite{Toussaint1980} is a
    subgraph of the Gabriel Graph. Two nodes \(i\) and \(j\) with
    distance \(d_{ij}\) are connected if no other node is in the
    \emph{lune}. The lune is defined as the intersection of two
    circles with radius \(r = d\) and centers on \(i\) and \(j\).
    See also Figure \ref{fig:lunes}\subref{sfig:lunes:def}.
    \begin{figure}[htbp]
        \centering
        \subfigure[Definition of the lunes][]{
                \label{sfig:lunes:def}
                \input{images/GG_RNG_def}
        }
        \subfigure[Gabriel graph example][]{
                \label{sfig:lunes:gg}
                \includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}
        }
        \subfigure[Relative Neighborhood graph example][]{
                \label{sfig:lunes:rng}
                \includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}
        }
        \caption[Gabriel - and Relative Neighborhood Graph]
                {\subref{sfig:lunes:def} Lunes of Gabriel Graph (red)
                    and Relative Neighborhood Graph (blue and red).
                 \subref{sfig:lunes:gg} Example of a Gabriel Graph.
                    Periodic nodes are dashed.
                 \subref{sfig:lunes:def} Example of a Relative
                    Neighborhood Graph. Periodic nodes are dashed.}
        \label{fig:lunes}

>>>>

%~ \subsubsection{Graphs}
    %~ A graph is a set of nodes \(V\) and edges \(E\).
\subsection{Gabriel- and Relative Neighborhood Graph}
\label{ssec:graphtypes}
    All here mentioned graph types are \emph{proximity graphs}. They are
    connecting nodes which are by some metric near to each other.
    Hence they are suited to generalize problems defined on regular
    lattices with nearest neighbor relationships, like the Ising model
    which will be described in more detail in section
    \ref{ssec:isingmodel}.\\
    The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
    Delaunay Triangulation. Two nodes \(i\) and \(j\) with distance
    \(d_{ij}\) are connected with an edge if a circle with it's
    center on the middlepoint between \(i\) and \(j\) and radius
    \(r = \frac d 2\) contains no other nodes. This area will be
    called \emph{lune} in the following. See also Figure
    \ref{fig:lunes}\subref{sfig:lunes:def}.\\
    The Relative Neighborhood Graph \cite{Toussaint1980} is a
    subgraph of the Gabriel Graph. Two nodes \(i\) and \(j\) with
    distance \(d_{ij}\) are connected if no other node is in the
    \emph{lune}. The lune is defined as the intersection of two
    circles with radius \(r = d\) and centers on \(i\) and \(j\).
    See also Figure \ref{fig:lunes}\subref{sfig:lunes:def}.
    \begin{figure}[htbp]
        \centering
        \subfigure[Definition of the lunes][]{
                \label{sfig:lunes:def}
                \input{images/GG_RNG_def}
        }
        \subfigure[Gabriel graph example][]{
                \label{sfig:lunes:gg}
                \includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}
        }
        \subfigure[Relative Neighborhood graph example][]{
                \label{sfig:lunes:rng}
                \includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}
        }
        \caption[Gabriel - and Relative Neighborhood Graph]
                {\subref{sfig:lunes:def} Lunes of Gabriel Graph (red)
                    and Relative Neighborhood Graph (blue and red).
                 \subref{sfig:lunes:gg} Example of a Gabriel Graph.
                    Periodic nodes are dashed.
                 \subref{sfig:lunes:def} Example of a Relative
                    Neighborhood Graph. Periodic nodes are dashed.}
        \label{fig:lunes}
